\RequirePackage{kvoptions-patch} % hack: allow newlines in kvoptions
\documentclass[11pt,letterpaper,oneside]{article}

\setcounter{secnumdepth}{0} % include unnumbered sections in ToC (and thereby, in PDF index)

\newcommand{\NotificationDate}{February 26, 2016}

\usepackage[
        Author={John A. Practitioner},
        AuthorRegistrationNumber={\#nn,nnn},
        AuthorAddress={Patent Firm\\
                       1600 Pennsylvania Ave NW\\
                       Washington, DC 20006},
        AuthorTelephone={(800) PAT-ENTS},
        Number={NN/NNN,NNN},
        FilingDate={January 1, 1970},
        FirstNamedInventorFirstName=John,
        FirstNamedInventorLastName=Browning,
        DocketNumber={XXXXX-XX},
        ConfirmationNumber=XXXX,
        Examiner={Suzy Q.},
        ExaminerTitle=Madam,
        ArtUnit=XXXX,
        NotificationDate={\NotificationDate},
        Title={METHODS AND SYSTEMS FOR PERPETUAL MOTION MACHINE},
        AmendmentDate={\today} %, % FIXME
        %Draft
]{officeaction}


% prior art short names
\newcommand{\xxxx}{{\em XXXX}\ }
\newcommand{\yyyy}{{\em YYYY}\ }

\begin{document}


\Title
        {In the United States Patent and Trademark Office}
        {Response to Non-Final Office Action of \NotificationDate{}}
        {\noindent{}MS Amendment\\
        Commissioner for Patents\\
        P.O. Box 1450\\
        Alexandria, VA 22313\textemdash{}1450\\}


\Intro

\Claims{%
        This listing of the claims replaces all prior versions and listings of
        the claims in the application.
}{%
\input{claims/01}

\claimbreak
\input{claims/04}

\claimbreak
\input{claims/09}

\claimbreak
\input{claims/12}

\claimbreak
\input{claims/17}

\claimbreak
\input{claims/19}

\claimbreak
\input{claims/24}

\claimbreak
\input{claims/26}

\claimbreak
\noindent{}Claims 31\textemdash{}82 (Canceled)
}


\Remarks{}{%

\subsection{Statement of Substance of Examiner Interview}

Applicant expresses sincere gratitude to Examiner Wang for the
courtesies extended to Applicant during the interview of XXXX.
The Examiner and Applicant's representatives discussed the invention,
the rejection under \ThirtyFiveUSCOneOhTwo{} and differences between the
invention and the cited prior art.  Applicant has amended the claims.

\subsection{Status of the claims}

At the time of the \OAem{}, claims ... were pending in the
application...

\subsubsection{Rejections and objections}
Claims ... stand rejected under
\ThirtyFiveUSCOneOhTwoAOne{} as allegedly anticipated by ...

Claims ...  stand objected to as depending from
a rejected base claim.

\subsubsection{Allowable Subject Matter}

The \OAem{} indicates that rewriting dependent claims ...  would place
claims ...  Applicant has rewritten these claims as recommended and
requests that the amended claims be allowed.

\subsubsection{Claim amendments}

Applicant herein amends independent claims ...; and rewrites dependent
claims ... in independent form including the limitations of each
respective dependent claim's base and intervening claims.

Applicant's claim amendments are supported by the application as
originally filed, for example at ...


%-----------------------------------------------------------------------
\subsubsection{Claim 1}

\input{argument/xxxx}
\input{argument/yyyy}


\subsubsection{Claims ...}

Regarding both \xxxx and \yyyy; each of independent
claims ... recite similar elements to those described above
with respect to claim 1.  Accordingly neither reference anticipates
those claims, and therefore, Applicant requests reconsideration and
withdrawal of the rejections.

Further, with respect to both \xxxx and \yyyy...

\section{Conclusion}

For the foregoing reasons, Applicant considers this application in good
and proper form for allowance.  The Examiner is respectfully requested
to pass this application to issue.  If in the Examiner's opinion a
telephone conference would expedite the prosecution of the subject
application then the Examiner is invited to call the undersigned
attorney.\\


} % REMARKS

\Signature


%\tableofcontents

\end{document}
